Lagrangian Space Nonlinear $E$-mode clustering

### 2016-11-25 ms_disp1/ms_disp1.tex
added MM code

\author{Hong-Ming Zhu}\email{hmzhu@bao.ac.cn}
\affiliation{Key Laboratory for Computational Astrophysics, National Astronomical Observatories, Chinese Academy of Sciences, 20A Datun Road, Beijing 100012, China}
\affiliation{University of Chinese Academy of Sciences, Beijing 100049, China}

@@

\subsection{Simulation}\label{ss.sim}
We use the open source cosmological simulation code {\tt CUBE} %\footnote{github link of cafcube}
\citep{cafcube}.
Cosmological parameters are set as
$\Omega_m=0.27$, $\Omega_\Lambda=0.73$, $h_0=0.68$, $n_s=0.96$ and $\sigma_8=0.83$.
Initial conditions are generated at redshift $z=50$ 
using Zel'dovich approximation, and using a CLASS transfer function.
$N_p=512^3$ $N$-body particles are evolved via 
their mutual gravitational interactions to $z=0$, in a periodic box with $L=400$ 
Mpc$/h$ per side. The code is set to use standard a particle-mesh (PM) algorithm 
\cite{1988csup.book.....H} on a two-level mesh grids
(details see \cite{2013MNRAS.436..540H}) and cloud-in-cell
(CIC) is used in particle interpolations in force 
calculation and obtaining the density field $\rho({\bs x})$ in Eulerian coordinates 
${\bs x}$ at late stages. We use density contrast $\delta\equiv\rho/\lb\rho\rb-1$ 
to describe the density fluctuations. The primordial linear density field $
\delta_L$ is given by the initial stage and scaled to $z=0$ by the linear growth 
factor. In the top and middle panels of Fig.1 we show projections of the nonlinear density field
$\delta_N$ given by the simulation and the linear density field $\delta_L$.
$\delta_N$ is obtained by the particle distribution at redshift $z=0$, and
the particles are interpolated by using the cloud-in-cell (CIC) algorithm.
Because $\delta_N$ is highly nonlinear and follows an approximate
log-normal distribution, we plot $\log_{10}(\delta_N+1)$ instead.
The nonlinear evolution of $\delta_N$ makes it very different from $\delta_L$
in appearance.

>>>>

\author{Hong-Ming Zhu}\email{hmzhu@nao.cas.cn}
\affiliation{Key Laboratory for Computational Astrophysics, National Astronomical Observatories, Chinese Academy of Sciences, 20A Datun Road, Beijing 100012, China}
\affiliation{University of Chinese Academy of Sciences, Beijing 100049, China}

@@

\subsection{Simulation}\label{ss.sim}
We use the open source cosmological simulation code {\tt CUBE} %\footnote{github link of cafcube}
\citep{cafcube}.
Cosmological parameters are set as
$\Omega_m=0.27$, $\Omega_\Lambda=0.73$, $h_0=0.68$, $n_s=0.96$ and $\sigma_8=0.83$.
Initial conditions are generated at redshift $z=50$ 
using Zel'dovich approximation, and using a CLASS transfer function
\citep{2011JCAP...07..034B}.
$N_p=512^3$ $N$-body particles are evolved via 
their mutual gravitational interactions to $z=0$, in a periodic box with $L=400$ 
Mpc$/h$ per side. The code is set to use standard a particle-mesh (PM) algorithm 
\cite{1988csup.book.....H} on a two-level mesh grids
(details see \cite{2013MNRAS.436..540H}) and cloud-in-cell
(CIC) is used in particle interpolations in force 
calculation and obtaining the density field $\rho({\bs x})$ in Eulerian coordinates 
${\bs x}$ at late stages. We use density contrast $\delta\equiv\rho/\lb\rho\rb-1$ 
to describe the density fluctuations. The primordial linear density field $
\delta_L$ is given by the initial stage and scaled to $z=0$ by the linear growth 
factor. In the top and middle panels of Fig.1 we show projections of the nonlinear density field
$\delta_N$ given by the simulation and the linear density field $\delta_L$.
$\delta_N$ is obtained by the particle distribution at redshift $z=0$, and
the particles are interpolated by using the cloud-in-cell (CIC) algorithm.
Because $\delta_N$ is highly nonlinear and follows an approximate
log-normal distribution, we plot $\log_{10}(\delta_N+1)$ instead.
The nonlinear evolution of $\delta_N$ makes it very different from $\delta_L$
in appearance.
